Attempting to write a full model

### 2016-09-13 R/misc/fullModel.rmd
done partnership

Seems like this model works?

>>>>

Seems like this model works? Now, let's test rcpp function...

```{r rcpp}
library(Rcpp)
sourceCpp("fullModel.cpp")

r1 <- lsoda(unlist(yini1), func = model1(HIVpars.mean), parms = HIVpars.mean, times = tvec)
r1rcpp <- lsoda(unlist(yini1), func = g, parms = expand(HIVpars.mean), times = tvec)
yini2 <- list(N = c(0.1, 0.2, 0.3), NN = matrix(c(0.1, 0.1, 0, 0,0,0,0,0,0), 3, 3))
yini3 <- calc_yini_full(HIVpars.mean)
tmpa <- unname(g2(0, unlist(yini3), expand(HIVpars.mean))$dSS)
tmpb <- unname(model2(expand(HIVpars.mean))(0, unlist(yini3), expand(HIVpars.mean))[[1]][67:75])
all.equal(tmpa, tmpb)
```
